A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-08 pilot-publication/lab-book.Rmd
Complete function to extract inline text from gt outcome tables

```{r setup}
library(pbapply)
library(openssl)
library(dotenv)
library(DataExplorer)
noacsr::source_all_functions()
```

@@

tables <- lapply(
    combined.outcome.results, function(ci.data) {
        {
            lapply(table.names, create_ci_level_tables, ci.data = ci.data)
        } %>%
            setNames(stringr::str_replace(table.names, pattern = "\\|\\|table\\:\\:", replacement = ""))
    }
)

## Save tables to file
document.string <- lapply(
    names(tables), function(ci.level.tables.name) {
        ## Extract confidence level as percentage
        ci.level <- stringr::str_remove(ci.level.tables.name, pattern = "ci\\.level\\.") %>%
            as.numeric() %>%
            scales::percent()
        ci.level.tables <- tables[[ci.level.tables.name]]
        paste0(
            "# ", ci.level, " confidence level\n\n",
            lapply(names(ci.level.tables), function(ci.level.table.name) {
                ci.level.table <- ci.level.tables[[ci.level.table.name]]
                paste0(
                    "## ", ci.level.table.name, "\n\n",
                    "\`\`\`{r, echo = FALSE} \n\n",
                    "tables[[\"", ci.level.tables.name, "\"]][[\"", ci.level.table.name, "\"]]", "\n\n",
                    "\`\`\`\n\n"
                )
            }) %>%
                paste0(collapse = "\n\n")
        )
    }
) %>%
    unlist() %>%
    paste0(collapse = "\n\n")

@@

```{r}
gt.table <- tables[[1]][[1]]
str(gt.table$`_data`, max.level = 1)
gt.table$`_data`
gt.table$`_styles`
```

>>>>

```{r setup}
noacsr::source_all_functions()
load_packages()
```

@@

tables <- lapply(
    combined.outcome.results, function(ci.data) {
        {
            lapply(table.names, create_ci_level_tables, ci.data = ci.data)
        } %>%
            setNames(stringr::str_replace(table.names, pattern = "\\|\\|table\\:\\:", replacement = ""))
    }
)
```

## Save tables to file

```{r}
## Save tables to file
document.string <- lapply(
    names(tables), function(ci.level.tables.name) {
        ## Extract confidence level as percentage
        ci.level <- stringr::str_remove(ci.level.tables.name, pattern = "ci\\.level\\.") %>%
            as.numeric() %>%
            scales::percent()
        ci.level.tables <- tables[[ci.level.tables.name]]
        paste0(
            "# ", ci.level, " confidence level\n\n",
            lapply(names(ci.level.tables), function(ci.level.table.name) {
                ci.level.table <- ci.level.tables[[ci.level.table.name]]
                paste0(
                    "## ", ci.level.table.name, "\n\n",
                    "\`\`\`{r, echo = FALSE} \n\n",
                    "tables[[\"", ci.level.tables.name, "\"]][[\"", ci.level.table.name, "\"]]", "\n\n",
                    "\`\`\`\n\n"
                )
            }) %>%
                paste0(collapse = "\n\n")
        )
    }
) %>%
    unlist() %>%
    paste0(collapse = "\n\n")

@@

```{r}
gt.table <- tables[[1]][[1]]
str(gt.table$`_data`, max.level = 1)
inline_outcome_text <- function(gt.table, outcome, level, column) {
    ## Define borrowed functions
    `%>%` <- magrittr::`%>%`
    pull <- dplyr::pull

    ## Check arguments
    assertthat::assert_that(
        "gt_tbl" %in% class(gt.table),
        is.character(outcome),
        is.character(level),
        is.character(column) | is.numeric(column)
    )

    ## Extract data
    gt.data <- gt.table$`_data`
    outcome.index <- na.omit(gt.table$`_styles`$rownum) # This relies on outcome names being styled as bold
    valid.outcomes <- gt.data$Outcome[outcome.index]
    outcome.pos <- grep(paste0("^", outcome, "$"), valid.outcomes)

    ## Stop if outcome not found
    if (length(outcome.pos) == 0) {
        stop(
            "No outcome found for outcome ",
            outcome,
            ". Choose one from c(",
            paste0(paste0("\"", valid.outcomes, "\""), collapse = ", "), ")."
        )
    }

    ## Extract only the relevant part of the table
    first.row <- outcome.index[outcome.pos] + 1
    if (outcome.pos == rev(outcome.index)[1]) {
        last.row <- nrow(gt.data)
    } else {
        last.row <- outcome.index[outcome.pos + 1] - 1
    }
    outcome.limits <- c(first.row, last.row)
    outcome.subtable <- gt.data[outcome.limits[1]:outcome.limits[2], ]

    ## Stop if column not found
    if (!is.numeric(column)) {
        new.column <- grep(column, names(outcome.subtable))
        if (length(new.column) > 1) {
            stop(
                "More than one column found for column ",
                column,
                ". Choose one from c(",
                paste0(paste0("\"", names(outcome.subtable), "\""), collapse = ", "), ")."
            )
        }
        if (length(new.column) == 0) {
            stop(
                "No column found for column ",
                column,
                ". Choose one from c(",
                paste0(paste0("\"", names(outcome.subtable), "\""), collapse = ", "), ")."
            )
        }
    }

    ## Stop if level not found
    new.level <- grep(level, outcome.subtable$Outcome)
    if (length(new.level) > 1) {
        stop(
            "More than one level found for level ",
            level,
            ". Choose one from c(",
            paste0(paste0("\"", outcome.subtable$Outcome, "\""), collapse = ", "), ")."
        )
    }
    if (length(new.level) == 0) {
        stop(
            "No level found for level ",
            level,
            ". Choose one from c(",
            paste0(paste0("\"", outcome.subtable$Outcome, "\""), collapse = ", "), ")."
        )
    }

    ## Extract inline text
    outcome.text <- outcome.subtable[outcome.subtable$Outcome == level, new.column] %>%
        pull() %>%
        unlist()

    ## Return inline text
    return(outcome.text)
}
gt.table$`_data`
gt.table$`_styles`
```
